
---
# title: "DATA 607 WEEK 9 ASSIGNMENT <br /> WORKING WITH NEW YORK TIMES WEB API AND JSON IN R"
# author: "[Kleber Perez - `r format(Sys.Date(), '%B %d, %Y')`](https://www.linkedin.com/in/kleberperez/)"
output: 
  html_document:
    code_folding: show
    theme: readable
    highlight: pygments
    css: ./w9css.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# 1. Library
library(kableExtra)
library(dplyr)
library(RCurl)
library(rjson)
library(RJSONIO)
library(jsonlite)

library(httr)
library(stringr)
library(ggplot2)

```

<div class="jumbotron jumbotron-fluid">
  <div class="btn btn-default btn-block">
  <br />
  
  <p><a class="label label-info" href="https://www.linkedin.com/in/kleberperez/" target="_blank" role="button">KLEBER PEREZ</a></p>
  <p class="lead">DATA 607 WEEK 9 ASSIGNMENT <br />WORKING WITH NEW YORK TIMES WEB API AND JSON IN R <br />
  SOURCE FILES AND RMARKDOWN ON 
   <a class="label label-warning" href="http://rpubs.com/kleberperez/477939" target="_blank" role="button">RPUBS</a>
   AND 
   <a class="label label-success" href="https://github.com/kleberperez1/CUNY-SPS-Data607-Project3" target="_blank" role="button">GITHUB</a>
  </p>
  
  <br />
  
  </div>
</div>

<br />

<div class="jumbotron jumbotron-fluid">
  <div class="btn btn-default btn-block">
  <br />
  
<div class="alert alert-info" role="alert">

  Using verb <a class="label label-default" href="https://developer.nytimes.com/docs/books-product/1/routes/reviews.json/get" target="_blank" role="button">GET (GET /reviews.json) from NYT</a></span> 
</div>
</div>

# <span id="maintop">Get book reviews

## Get New York Times lookup book reviews.

<div class="alert alert-info" role="alert">

  The New York Times Developer Network page provides a rich set of APIs, as described 
  <a class="label label-default" href="https://developer.nytimes.com/" target="_blank" role="button">here</a> 
  <br />
  
  <a class="label label-default" href="https://developer.nytimes.com/get-started" target="_blank" role="button">Get started</a>
  using the APIs in four steps: <br />
  1. Create an Account <br />
  2. Sign In <br />
  3. Register apps <br />
  4. Access the API keys <br />

  The <a class="label label-default" href="https://developer.nytimes.com/apis" target="_blank" role="button">APIs</a> 
  page has information on the different APIs. The documentation for each API includes an interactive reference for trying out the
  API.

</div> 
</div>

<br />

##  In this exercise, I choose the New York Times Book Reviews API to construct an interface in R to read in the JSON data, and transform it to an R dataframe. 

```{r}
jsonFile <- "https://api.nytimes.com/svc/books/v3/reviews.json?author=Stephen+King&api-key=jJ91v5ccDG0o0FKdjaaN8JjNk2h3iIwq"
#isValidJSON(jsonFile)

jsonR <- tbl_df(as.data.frame(fromJSON(jsonFile)))
jsonR %>% kable() %>% 
  kable_styling(bootstrap_options = "striped", font_size = 10) %>% 
  scroll_box(height = "500px", width = "100%")

```

<br />

<a href="#maintop">Go to top</a>

<br /><br />

* * *

<br /><br />

<div class="jumbotron jumbotron-fluid">

## Conclusion

<div class="alert alert-info" role="alert">

The book reviews service lets you get NYT book review by author, ISBN, or title.
The New York Times Book reviews API lets you get data from all New York Times Book reviews including rank history for specific reviews.

</div>

<div class="btn btn-default btn-block">

  <p class="lead">SOURCE FILES AND RMARKDOWN ON 
   <a class="label label-warning" href="http://rpubs.com/kleberperez/477939" target="_blank" role="button">RPUBS</a>
   AND 
   <a class="label label-success" href="https://github.com/kleberperez1/CUNY-SPS-Data607-Project3" target="_blank" role="button">GITHUB</a>
  </p>

</div>
</div>

<a href="#maintop">Go to top</a>

<br /><br />


* * *

<br /><br />

> *Please email to: * <a href="mailto:kleber.perez@live.com">Kleber Perez</a> *for any suggestion.*

<footer class="border-top text-muted fixed-bottom">

        DATA 607 Week 9 Assignment - MSDS 2019 Program.

</footer>

\textbf{Text ignored: END of other links}

<br />
<br />
<br />


